---
site: blogdown:::blogdown_site
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center")
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
```



# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries.


```{r, load_alcohol_data, cache=FALSE}
library(fivethirtyeight)
data(drinks)

```



**There are four numeric variables: *beer_servings*, *spirit_servings*, *wine_servings*, and *total_liters_of_pure_alcohol*. There is one character variable, *country*. There are no missing values.**


```{r glimpse_skim_data}

glimpse(drinks)
skim(drinks)
```




```{r beer_plot}
top25_beer <- top_n(drinks, 25, beer_servings)

ggplot(data = top25_beer, mapping = aes (y = reorder(country, beer_servings), x = beer_servings)) + geom_col(fill='dark orange') +
  labs(title = "Top 25 Beer Consuming Countries", subtitle = "Namibians are leading beer consumers.", x = "Beer Servings", y = "") +
  geom_text(aes(label= beer_servings), vjust=0.3, hjust = 1.3,  color="white", size=3) +
  theme_clean()
NULL

  
```


```{r wine_plot}
top25_wine <- top_n(drinks, 25, wine_servings)
ggplot(data = top25_wine, mapping = aes (y = reorder(country, wine_servings), x = wine_servings)) +   geom_col(fill='dark red') +
  geom_text(aes(label= wine_servings), vjust=0.3, hjust = 1.3,  color="white", size=3) +
labs(title = "Top 25 Wine Consuming Countries", x = "Wine Servings", y = "") +
  theme_clean() +
  
NULL

```


```{r spirit_plot}
top25_spirits <- top_n(drinks, 25, spirit_servings)
ggplot(data = top25_spirits, mapping = aes (y = reorder(country, spirit_servings), x = spirit_servings))+
  geom_col(fill='light blue') + 
  geom_text(aes(label= spirit_servings), vjust=0.3, hjust = 1, color="black", size=3) +
  labs(title = "Top 25 Spirits Consuming Countries", y = "", x = "Spirits Servings") +
  theme_clean() +
  
NULL 
 

```

**Country vs Beer consumption** bar charts show that beer is the most popular in Eastern European, African, and Central American countries. Furthermore, **Country vs Spirit Consumption** shows that spirits tend to be popular in Eastern European and some Asian countries as well as on islands. On the other hand, based on the **Country vs Wine consumption** bar chart, wine is popular in Western European, Scandinavian, and South American countries.
Overall, the bar charts show two trends. First one is that countries that are large exporters of a certain product tend to be among the countries that consume it the most. For example France and Portugal are among the top wine consuming countries, Czech Republic is the second in the beer chart, whereas Russia and Belarus are among the top countries for spirits consumption (which includes Vodka for example). It also seems that overall more developed countries enjoy more wine consumption, whereas less developed countries enjoy more beer and spirits consumption. This is expected as wine is usually more expensive and can be associated with prestige (especially if it is old!).


